\begin{center}
  {\large \bf Self-Recognition-based of Modular Legged Robot} 
  
  {\large \bf} Tharit Sinsunthorn
\end{center}

\begin{center}
  \LARGE \bf Abstract
\end{center}

In the expansive domain of lunar exploration, where the rugged lunar terrain and harsh environmental conditions present formidable challenges, the pursuit of innovative robotic solutions has intensified. Modular legged robots have emerged as a promising frontier, offering unparalleled adaptability and maneuverability in navigating the diverse lunar landscapes.

This thesis introduces "Moonbot", a modular legged robot to transcend the limitations of traditional lunar exploration missions. Developed as part of the prestigious Moonshot project led by the Space Robotics Laboratory at Tohoku University. Moonshot project has a strong aiming to develop a modular robot with the implementation of plug-and-play AI system for the propose of solar panels and lunar based construction. Henceforth, Moonbot stands as the pioneering prototype, embodying and extending the conceptual framework for robotic operations across lunar terrains. Its inception marks a pivotal moment in the evolution of robotic exploration, illuminating new pathways and possibilities for traversing and navigating the lunar landscape with unprecedented efficiency and adaptability.

Moonbot's innovative design is characterized by its self-recognition-based motion control capabilities, allowing dynamic adaptability to various leg configurations, from solitary to quadrupedal stances. Central to its design philosophy is a flexible structure, facilitated by magnetic connections between modular components, enabling rapid reconfiguration to meet evolving mission requirements.

Within the Moonshot project framework, Moonbot serves as a pioneering platform for testing and validating novel robotic technologies for lunar exploration and lunar base construction. Its modularity extends to independent leg controllers seamlessly integrated within the Robot Operating System 2 (ROS2) framework, ensuring seamless communication and precise control.

As Moonbot continues to undergo rigorous testing and refinement, it represents a significant leap forward in the quest for innovative robotic solutions for lunar exploration and beyond. With its adaptable design and robust capabilities, Moonbot embodies the spirit of exploration and innovation driving the Moonshot project, paving the way for future advancements in lunar robotics and space exploration.

\bigskip



\clearpage


% Add more content as needed

