

\begin{thebibliography}{99}
\itemsep 3mm{
	
	%著者１，著者２：`` 題目 ''，学会名(出版社)，西暦
	%
	%author1, author2: `` title '', conference, year
	
	%\bibitem{}
	%	氏 名：
	%	`` 題目 ''，
	%	学会名(出版社)，
	%	西暦

	\bibitem{GLXP}
	Google Lunar XPRIZE公式ホームページ, http://lunar.xprize.org/

	\bibitem{hakuto}
	チームHAKUTO公式ホームページ, http://team-hakuto.jp/

	\bibitem{lava-tube1}
		Haruyama J., Sawai S., Mizuno T., Yoshimitsu T., Fukuda S., Nakatani I., 
			``Exploration of Lunar Holes, Possible Skylights of Underlying Lava Tubes, by Smart Lander for Investigating Moon (SLIM)'',
				Transactions of the Japan Society for Aeronautical and Space Sciences, Aerospace Technology Japan, vol. 10, pp. Pk\_7-Pk\_10, 2012.

	\bibitem{lava-tube2}
		Samuel J., Julie D., B. Ray Hawke, Benjamin T., Joshua T. S., Joshua L., Bradley L., Brett W., Mark S., Timothy D., D. Benjamin J., Paul D., Thomas A., W. Brent Garry, 
			``LRO observations of morphology and surface roughness of volcanic cones and lobate lava flows in the Marius Hills'', Journal of Geophysical Research, Volume 118, Issue 4, pp. 615-634, 2013.

	\bibitem{HAKUTOmission}
		Britton N., Yoshida K., Walker J., Nagatani K., Taylor G., Dauphin L., 
			``Lunar micro rover design for exploration through virtual reality tele-operation'', 
				Proceedings of the 9th Conference on Field Service and Robotics, pp. 1-14, 2013.

	\bibitem{ToFprinciple}
		Miles H., Seungkyu L., Ouk C., Radu H., 
			{\it ``Time of Flight Cameras: Methods, and Applications''}, 
				Springer, 2012.

	\bibitem{robotToF}
	Stephan H., Thorsten L., 
		``Robot Vision System based on a 3D-TOF Camera'', 
			Proceedings of IEEE Instrumentation \& Measurement Technology Conference IMTC, pp. 1-5, 2007.	

	\bibitem{robotToF2}
	Guillem A., Sergi F., Carme T.,
		``ToF Cameras for active vision in robotics'', 
			Sensors and Actuators A: Physical, Volume 218, pp. 10-22, 2014.

	\bibitem{Takuto-san-paper}
	Oikawa T., Tanaka T., Walker J., Uno K., Costa P., Britton N., Yoshida K.,
		``Thermal design and analysis of conceptual fright model of lunar exploration rover'', 
			Proceedings of the 13th i-SAIRAS, 2016.

	\bibitem{reflectance_of_regolith}
		Heiken G.H., Vaniman D.T., French B.M., 
			{\it ``Lunar Source book''}, 
				Cambridge University Press, 1991.	
	
	\bibitem{solar-irradiance}
		Hulstrom R., Bird R., Riordan C., 
			``Spectral solar irradiance data sets for selected terrestrial conditions'', 
				Solar Cells, Volume 15, pp. 365-391, 1985.

	\bibitem{Higa-san-paper}
		Higa S., Nagaoka K., Yoshida K., 
			``Online estimation of wheel sinkage and slippage using a ToF camera on loose soil'', 
			 Proceedings of the ISTVS 8th Americas Regional Conference, accepted, 2016.

	\bibitem{NIST}
		NIST, Standard Test Methods For Response Robot, ``Guide for Evaluating, Purchasing, and Training with Response Robots　Using DHS-NIST-ASTM International Standard Test Method'', https://www.nist.gov/programs-projects/department-homeland-security-response-robot-performance-standards (accessed on 9/2/2016).
		


}
\end{thebibliography}

