%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%
%%%  謝辞
%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{my_ack}
This book was created at the Space Robotics Laboratory, Faculty of Engineering, Tohoku University and supported by JST Moonshot R\&D Program, Grant Number JPMJMS223B.

I extend my sincere appreciation to the Space Robotics Laboratory of Prof. Kazuya Yoshida, where I have had the privilege of conducting my research. I am deeply grateful for the mentorship, guidance, and opportunities provided by Prof. Yoshida and the lab members, which have been invaluable to my growth and development in the field of robotics.

I am indebted to Assistant Prof. Uno Kentaro and Prof. Shreya Santra for their invaluable support and guidance throughout my journey. Assistant Prof. Uno's insights and advice on legged robotics have been instrumental in shaping my understanding of this complex field, while Prof. Shreya's support in ideation and thesis writing has been invaluable.

I would like to express my heartfelt thanks to Danish AI for his exceptional work in developing the hardware design of Moonbot. Additionally, I extend my gratitude to Pascal Pama and Torii Keigo for their support during experiments and their insightful comments on my work.

Special thanks are due to Gustavo Diaz for his significant contributions to Moonshot project team. His advice on robot software development and debugging has been invaluable to our progress.

I am deeply grateful to the Limbing Robotics team for their invaluable contributions to my understanding of legged robotics. Their expertise and knowledge-sharing have been instrumental in shaping my understanding of this complex field. Special thanks are due to the Limbero climbing quadruped robot team, whose insights and advice on Moonbot's software development have been invaluable to our project's success.

I would also like to express my sincere appreciation to Uchida Akiyoshi of the Orbital Robotics team for his assistance with ROS2 control. His guidance and support have been instrumental in navigating the intricacies of robotic control systems, enabling us to enhance Moonbot's capabilities.

Additionally, I extend my gratitude to Nagaoka Keita for his support with video shooting, which has been essential in documenting and sharing our project's progress effectively.

To each of these individuals and teams, I offer my deepest thanks for their invaluable contributions, guidance, and support, which have significantly enriched my journey in robotics and contributed to the success of the Moonshot project.

\begin{flushright}
February, 2024\\
Tharit Sinsunthorn
\end{flushright}
\end{my_ack}
%%%  EOF %%%